\textbf{NAME OF THIS STUDY}

### 2019-10-13 submission/manuscript.tex
Optimized pipeline for reduced no. of samples.
Added ATCC reference database
Optimization of pdf generation

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

@@

\usepackage{helvet} % Helvetica font
\renewcommand*\familydefault{\sfdefault} % Use the sans serif version of the font
\usepackage[T1]{fontenc}

@@

\newpage
\linenumbers

\hypertarget{abstract}{%
\subsection{Abstract}\label{abstract}}

@@

\hypertarget{introduction}{%
\subsection{Introduction}\label{introduction}}

\hypertarget{results-and-discussion}{%
\subsection{Results and Discussion}\label{results-and-discussion}}

\hypertarget{conclusions}{%
\subsection{Conclusions}\label{conclusions}}

\hypertarget{materials-and-methods}{%
\subsection{Materials and Methods}\label{materials-and-methods}}

@@

\hypertarget{references}{%
\subsection{References}\label{references}}

>>>>

% Create subtitle command for use in maketitle
\providecommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

@@

\usepackage{times} % Times New Roman font
\usepackage[T1]{fontenc}

@@

@@

\linenumbers

\subsection{Abstract}\label{abstract}

\subsection{Introduction}\label{introduction}

\subsection{Results and Discussion}\label{results-and-discussion}

\subsection{Conclusions}\label{conclusions}

\subsection{Materials and Methods}\label{materials-and-methods}

@@

\subsection{References}\label{references}
